Meta-analysis of the Interoceptive Accuracy Scale

### 2025-08-29 analysis/Study1.qmd
updated analysis scripts

- **Sample 1a**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 1, downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2[c("Age", "Gender")], age = "Age", sex = NA, gender = "Gender")`.
- **Sample 3**: Data from [Campos's(2022)](https://osf.io/j6ef3) study, downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 4**: Data from [Todd's(2022)]( https://osf.io/ms354/) study, downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5_attention, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 6**: Data from [Brand's(2022)](https://osf.io/xwz6g/) study, downloaded from OSF, included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7a**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7b**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7c**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7c, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8a**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 11**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df11 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 12**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df12 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 13**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df13 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 14**: Data from [Poreiro's(2024)](https://osf.io/49wbv) study , included `r report::report_participants(df14 , age = "Age", sex = NA, gender = "Gender")`
- **Sample 15 **: Data from [Poreiro's] study , included `r report::report_participants(df15 , age = "Age", sex = NA, gender = "Gender")`
- **Sample 16 **: Data from [Arjona's] study , included `r report::report_participants(df16 , age = "Age", gender = "Gender")`

>>>>

- **Sample 1a**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 1, downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2[c("Age", "Gender")], age = "Age", sex = NA, gender = "Gender")`.
- **Sample 3**: Data from [Campos's(2022)](https://osf.io/j6ef3) study, downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 4**: Data from [Todd's(2022)]( https://osf.io/ms354/) study, downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5_attention, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 6**: Data from [Brand's(2022)](https://osf.io/xwz6g/) study, downloaded from OSF, included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7a**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7b**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7c**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7c, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8a**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 11**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df11 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 12**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df12 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 13**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df13 , age = "Age", sex = NA, gender = "Gender")`.
- **Sample 14**: Data from [Poerio's(2024)](https://osf.io/49wbv) study , included `r report::report_participants(df14 , age = "Age", sex = NA, gender = "Gender")`
- **Sample 15 **: Data from [Poerio's] study , included `r report::report_participants(df15 , age = "Age", sex = NA, gender = "Gender")`
- **Sample 16 **: Data from [Arjona's] study , included `r report::report_participants(df16 , age = "Age", gender = "Gender")`

### 2025-08-29 analysis/study2.qmd
updated analysis scripts

average_corr <- data |>
  summarise(min_r = min(r, na.rm = TRUE), 
            mean_r = mean(r, na.rm = TRUE),
            max_r = max(r, na.rm = TRUE), 
            Max = var_Interoception[which.max(abs(r))],
            .by=c("Component", "var_Correlate"))

@@

average_corr <- data |>
  summarise(
    min_r = min(r, na.rm = TRUE), 
    mean_r = mean(r, na.rm = TRUE),
    max_r = max(r, na.rm = TRUE), 
    Max = var_Interoception[which.max(abs(r))],
    n_sig_001 = sum(p < .001, na.rm = TRUE),
    n_sig_01  = sum(p < .01 & p >= .001, na.rm = TRUE),
    n_ns      = sum(p >= .01 | is.na(p)),
    total     = dplyr::n(),
    .by=c("Component", "var_Correlate")
  ) |>
  mutate(
    perc_sig = (n_sig_001 + n_sig_01) / total
  )
sort(table(average_corr$Max), decreasing = TRUE)

>>>>

average_corr <- data |>
  summarise(min_r = min(r, na.rm = TRUE), 
            mean_r = mean(r, na.rm = TRUE),
            max_r = max(r, na.rm = TRUE), 
            Max = var_Interoception[which.max(abs(r))],
            .by=c("Component", "var_Correlate")) 
#   
# average_corr <- data |>
#   summarise(
#     min_r = min(r, na.rm = TRUE), 
#     mean_r = mean(r, na.rm = TRUE),
#     max_r = max(r, na.rm = TRUE), 
#     Max = var_Interoception[which.max(abs(r))],
#     n_sig_001 = sum(p < .001, na.rm = TRUE),
#     n_sig_01  = sum(p < .01 & p >= .001, na.rm = TRUE),
#     n_ns      = sum(p >= .01 | is.na(p)),
#     total     = dplyr::n(),
#     .by=c("Component", "var_Correlate")
#   ) |>
#   mutate(
#     perc_sig = (n_sig_001 + n_sig_01) / total
#   )

@@
